A simplified dynamic bioenergetic model for coral-algal symbiosis and coral bleaching

### 2016-10-27 JTB_ms/JTB_ms.tex
abstract

  \begin{abstract}
  This is the abstract. Some type of positive feedback is necessary.
  Compare scenarios of recycling CO2, have photodamage increase
  maintenance that does recycle CO2. Compare recycled N to symbiont
  instead of host How much do you have to reduce the light to get
  recovery? i.e., magnitude of hysteresis?
  \end{abstract}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig1.png}
\caption{Graphical representation of coral-algal symbiosis model. Light,
CO\textsubscript{2}, prey, and DIN are acquired from the external
environment proportional to the biomass of the partner indicated by the
black box for uptake. Mass fluxes (see Table 1 for definitions) are
represented by \(j\)'s with subscripts indicating the type of mass, and
in some cases the process (e.g., \(j_{CP}\) is the flux of carbon
produced by photosynthesis), and \(\rho\)'s indicate fluxes that are
shared by one partner with the other. Parallel complementary
synthesizing units (SUs) are represented by large circles, and rejection
fluxes from these SUs are indicated by dashed lines. \(c_{ROS}\) is a
proportional rate that impacts other model fluxes by inhibition or
acceleration; likewise, \(j_{eC}\) accelerates the rate of \(j_{CO_2}\).
Recycled mass fluxes from biomass turnover are not shown for clarity
(but see Table 1 for definitions).}
\end{figure}

@@

\begin{equation} r_{CH}=\sigma_{CH}j_{HT}^0 \end{equation}\begin{equation} r_{CS}=\sigma_{CS}j_{ST}^0 \end{equation}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Steady state values of \textbf{A)} specific growth (Cmol
Cmol\textsuperscript{-1} d\textsuperscript{-1}), \textbf{B)} the
symbiont to host biomass ratio (CmolS CmolH\textsuperscript{-1}),
\textbf{C)} relative C- or N-limitation of host biomass formation, and
\textbf{D)} relative CO\textsubscript{2}- or light-limitation of
symbiont photosynthesis, across gradients of external irradiance and
dissolved inorganic nitrogen. Note that typical conditions for reefs are
\textasciitilde{}1e-7 M DIN and 10-20 mol photons m\textsuperscript{-2}
d\textsuperscript{-1}. Simulations for each combination of light and
nutrients (41 points along each axis) were run for 100 days with a time
step of 1 day. Negative steady state growth rates, and corresponding S:H
ratios, were set to zero.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig3.png}
\caption{Sensitivity analysis. Plots show the fractional change in
steady state values of growth (solid lines) and S:H biomass (dashed
lines) in response to fractional changes in default parameter values
(see Table 2 for default values). Parameters are grouped by which
processes they are involved in. This sensitivity analysis was conducted
at conditions typical for coral reef environments: low DIN (1e-7 M) and
intermediate light (15 mol m\textsuperscript{-2} d\textsuperscript{-2}).
Sensitivity analyses conducted other environmental conditions are
presented in the Supplementary Information.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig4.png}
\caption{Figure 4. Light-driven seasonal dynamics of symbiont abundance
and coral growth. Light input (upper panel) was designed as a sinusoidal
curve with a period of one year, with maximum and minimum values of 40
and 22 mol photons m\textsuperscript{-2} d\textsuperscript{-1}, based on
Stimson (1997). The dynamic behavior of symiont to host biomass ratio
(middle panel) and the specific growth rate of host biomass (lower
panel) show seasonal oscillations that are greater in magnitude under
higher nutrients (1e-5 molN L\textsuperscript{-1}; dashed lines)
relative to lower nutrients (1e-7 molN L\textsuperscript{-1}; solid
lines), consistent with the findings of Stimson (1997). Prey density was
set at 1e-5 CmolX L\textsuperscript{-1}.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig5.png}
\caption{Figure 5. Bleaching.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig6.png}
\caption{Figure 6. Bleaching and interactive factors.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig7.png}
\caption{Figure 7. Hysteresis.}
\end{figure}

>>>>

  \begin{abstract}
  Coral reef ecosystems owe their ecological success--and vulnerability to
  climate change--to the symbiotic metabolism of corals and
  \emph{Symbiodinium} spp. The urgency to understand and predict the
  stability and breakdown of these symbioses (i.e., coral `bleaching')
  calls for the development and application of theoretical tools. While
  the biological complexity of the symbiosis is well-suited to dynamical
  modeling, the theoretical complexity of certain approaches makes them
  inaccessible to many biologists, thus limiting their potential
  application and utility. Here, we develop a simplified dynamic
  bioenergetic model of coral-algal symbiosis that demonstrates realistic
  steady-state behavior across gradients of light, nutrients, and feeding.
  Furthermore, through a mechanistic treatment of photo-oxidative stress,
  the model displays dynamic responses of bleaching and recovery, and
  suggests that these phenomena represent transitions between alternative
  stable states. A suite of complex observed behaviors reproduced by this
  model suggests it has captured many important attributes of the system;
  meanwhile, its modular framework and open source R code are designed to
  facilitate expansion and problem-specific applications. We see high
  utility for this model in elucidating the mechanistic underpinnings of
  complex responses, generating testable hypotheses, and predicting
  integrated responses to simultaneous changes in multiple environmental
  inputs.
  \end{abstract}

@@

\includegraphics{../img/Fig1.png}

@@

\begin{equation} r_{CH}=j_{HT}^0 \cdot {S \over H} \end{equation}\begin{equation} r_{CS}=\sigma_{CS}j_{ST}^0 \end{equation}

@@

\includegraphics{../img/Fig2.png}

@@

\includegraphics{../img/Fig3.png}

@@

\includegraphics{../img/Fig4.png}

@@

\includegraphics{../img/Fig5.png}

@@

\includegraphics{../img/Fig6.png}

@@

\includegraphics{../img/Fig7.png}
